### 2017-02-14 R/cambridge.Rmd
Updated .gitignore and cambridge.Rmd

```{r libs, eval = TRUE, echo = TRUE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
rm(list=ls())
library("devtools")
install_github("syounkin/ITHIM", ref="devel")
#install("~/ITHIM/")
#document("~/ITHIM/")
#install("~/ITHIM/")
library("ITHIM")
```

>>>>

```{r libs, eval = TRUE, echo = TRUE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
rm(list=ls())
library("devtools")
#install_github("syounkin/ITHIM", ref="cambridge")
install("~/ITHIM/")
document("~/ITHIM/")
install("~/ITHIM/")
library("ITHIM")
```
